\textbf{{C++ Developer, Compilers Department ISP RAS} \hfill September 2022 - December 2023}\par

\begin{itemize}
    \textbf{{Clang-Tidy/Clang Static Analyzer} \hfill September 2022 - June 2023} \\
  The main task was to write static checks and improve the overall C/C++ code analysis infrastructure. In addition to the simple implementation of verification, it was necessary to optimize the algorithm as much as LLVM tools allowed. \\

    \textbf{{LLVM Backend for PowerPC} \hfill June 2023 - December 2023}\\
    The main task was to add a new backend to the LLVM compiler infrastructure. Adding a new backend means adding new instructions and a set of registers to the existing LLVM infrastructure. There was also a need to add support for address sanitizer for this architecture.
\end{itemize} \par

\textbf{{C++ Developer, Yandex} \hfill January 2024 - March 2025} \par
\begin{itemize}
I worked in the Yandex Market search and data preparation infrastructure department. I have been optimizing highly loaded services, such as the introduction of new technologies and the review of service logic.
One of the tasks was to rewrite the legacy service, which resulted in multiple performance gains.
\end{itemize}

\textbf{{Research Developer, Kaspersky} \hfill March 2025 - Present}
\begin{itemize}
    At Kaspersky, I do performance analysis. My responsibilities include product testing and profiling, architecture analysis and optimization. I also develop the internal infrastructure. I have experience working with eBPF and various profiling tools.   
\end{itemize}